Critical Temperature of Superconductors YBCO and BSCCO

### 2014-11-19 Draft.tex
intro

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.
In 1911, certain types of metals at temperatures around 10 K were found to exhibit superconductivity, that is, their electrical resistance became zero. 
The temperature at which this loss of resistance occurs is called the critical temperature.

>>>>

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.
In 1911, Kamerlingh Onnes discovered superconductivity in mercury.  
Instead of a gradual decrease in the electrical resistance as the temperature decreased, he found a sudden loss of resistance when the temperature went below 4.2 K. 
The temperature at which the resistance disappears is called the critical temperature.
In addition to having no resistance, superconductors also exhibit perfect diamagnetism, so it excludes magnetic field flux. 
This property, called the Meissner effect, was found in 1933.

%certain types of metals at temperatures around 10 K were found to exhibit superconductivity, that is, their electrical resistance became zero. 
%The temperature at which this loss of resistance occurs is called the critical temperature.
